Information Disclosure in Dynamic Innovation Contests

### 2025-04-29 paper/Paper.tex
update-paper

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $(y, t) \in\mathbb{R}\times[0, T)$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(y, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = y / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
\end{lemma}

@@

%% Data: Leaderboard
The third component of the observed data is an open leaderboard that records the real-time rankings and scores of each participant, denoted by $\hat{x}^i_t$. 
We interpret the difference in scores between $i$ and $j$ displayed on the leaderboard as the signal $Z_t$ (defined in (\ref{signal})) released by the contest organizer. 
Specifically, let's denote $\hat{y}_t = \hat{x}^i_t - \hat{x}^j_t$ the gap between displayed scores, and interpret it as the signal intentionally released by the contest organizer: 
\begin{equation}\label{eq-model-signal}
dZ_t = \hat{y}_tdt
\end{equation}
As indicated in (\ref{signal}), we assume that $\hat{y}_t$ represents a noisy signal, with its precision governed by $\lambda$.
Moreover, according to (\ref{eq-state-dynamics}), the observed real-time gap $\hat{y}_t$ on leaderboard evolves as 
\begin{equation}\label{eq-leaderboard-gap}
d\hat{y}_t = \left[m_i(\tilde{y}_t, t) - m_j(\tilde{y}_t, t)\right]dt + \sigma dW_{t} + \frac{dB_t}{\sqrt{\lambda}}
\end{equation}
where the term $\sigma dW_t$ captures the innovation shock, and $dB_t/\sqrt{\lambda}$ represents the signal noise.
These two types of uncertainty can be consolidated into a unified source $\sqrt{\sigma^2 + 1/\lambda}d\hat{W}_t$, where $\hat{W}_t$ is a Brownian motion. 
It is important to recognize that the generation of $\hat{y}_t$ is inherently tied to the players’ strategic interactions, as it depends on their estimates of the underlying state, $\tilde{y}_t$. 
In turn, $\tilde{y}_t$ evolves dynamically based on $\hat{y}_t$, since players continually update their beliefs in response to observed data. 
As a result, the generation of $\hat{y}_t$ and $\tilde{y}_t$ proceeds jointly.
By (\ref{filtered-x}) and (\ref{eq-model-signal}), the estimated gap $\tilde{y}_t$ by the two players is jointly generated by 
\begin{equation}\label{eq-fintered-y-update}
d\tilde{y}_{t} = (q_{i,t}-q_{j,t})dt + \sqrt{\lambda}\sigma(\hat{y}_t-\tilde{y}_{t}) dt
\end{equation}

@@

Suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Moreover, we assume that the sampling occurs at fixed time intervals $t_{k+1}-t_k$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ follows $\mathcal{N}(\mu_0, \sigma_0)$. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}
\begin{aligned}
p&\left(\{\hat{y}_{t_k}\}_{k=1}^N)| m_i, m_j\right) = 
\phi\left(y_0 | \mu_0, \sigma_0\right) \times\\
&\quad\prod_{k=0}^{N-1}\phi\left(\hat{y}_{t_{k+1}}-\hat{y}_{t_k}|\int_{t_k}^{t_{k+1}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds, \left(\sigma^2+\frac{1}{\lambda}\right)(t_{k+1}-t_k)\right)
\end{aligned}
\end{equation}

@@

\begin{algorithm}
\caption{Synthetic Data Simulation}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$, $y_0$, $\tilde{y}_0$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from homogeneous Poisson process $(\tau^\star_{i(j)})$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample $\{.\}$
\STATE Initialize $\ell^{i(j)}=0$, $\hat{y}_0 = 0$, $\tilde{y}_t=0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta t)$} 
        \IF {$u_k^{i(j)} > \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta t} \gets $ (\ref{eq-leaderboard-gap})
        \ENDIF
    \ENDFOR
    \STATE $\tilde{y}_{t+\Delta t}$ $\gets$ (\ref{eq-fintered-y-update})
\ENDFOR
\STATE Fill in all missing entries in $(\hat{y}_t)$ by propagating the last observed value.
\STATE \textbf{Output:} $(\tilde{y}_t)$, $(\hat{y}_t)$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(m_{i(j)}(\tilde{y}_t, t))$
\end{algorithmic}
\end{algorithm}

>>>>

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(y, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(y, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = y / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
\end{lemma}

@@

%% Data: Leaderboard
The third component of the observed data is an open leaderboard that records the real-time rankings and scores of each participant, denoted by $\hat{x}^i_t$. 
We interpret the difference in scores between $i$ and $j$ displayed on the leaderboard as the signal $Z_t$ (defined in (\ref{signal})) released by the contest organizer. 
Specifically, let's denote $\hat{y}_t = \hat{x}^i_t - \hat{x}^j_t$ the gap between displayed scores, and interpret it as the signal intentionally released by the contest organizer: 
\begin{equation}\label{eq-model-signal}
dZ_t = \hat{y}_tdt
\end{equation}
As indicated in (\ref{signal}), we assume that $\hat{y}_t$ represents a noisy signal, with its precision governed by $\lambda$.
Moreover, according to (\ref{eq-state-dynamics}), the observed real-time gap $\hat{y}_t$ on leaderboard evolves as 
\begin{equation}\label{eq-leaderboard-gap}
d\hat{y}_t = \left[m_i(\tilde{y}_t, t) - m_j(\tilde{y}_t, t)\right]dt + \sigma dW_{t} + \frac{dB_t}{\sqrt{\lambda}}
\end{equation}
where the term $\sigma dW_t$ captures the innovation shock, and $dB_t/\sqrt{\lambda}$ represents the signal noise.
It is important to recognize that the generation of $\hat{y}_t$ is inherently tied to the players’ strategic interactions, as it depends on their estimates of the underlying state, $\tilde{y}_t$. 
In turn, $\tilde{y}_t$ evolves dynamically based on $\hat{y}_t$, since players continually update their beliefs in response to observed data. 
As a result, the generation of $\hat{y}_t$ and $\tilde{y}_t$ proceeds jointly.
By (\ref{filtered-x}) and (\ref{eq-model-signal}), the estimated gap $\tilde{y}_t$ by the two players is jointly generated by 
\begin{equation}\label{eq-fintered-y-update}
d\tilde{y}_{t} = \left[m_i(\tilde{y}_t, t) - m_j(\tilde{y}_t, t)\right]dt + \sqrt{\lambda}\sigma(\hat{y}_t-\tilde{y}_{t}) dt
\end{equation}

@@

Suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Moreover, we assume that the sampling occurs at fixed time intervals $t_{k+1}-t_k$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ follows $\mathcal{N}(\mu_0, \sigma_0)$. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}
\begin{aligned}
p&\left(\{\hat{y}_{t_k}\}_{k=1}^N | m_i, m_j\right) = 
\phi\left(y_0 | \mu_0, \sigma_0\right) \times\\
&\quad\prod_{k=0}^{N-1}\phi\left(\hat{y}_{t_{k+1}}-\hat{y}_{t_k}|\int_{t_k}^{t_{k+1}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds, \left(\sigma^2+\frac{1}{\lambda}\right)(t_{k+1}-t_k)\right)
\end{aligned}
\end{equation}

@@

\begin{algorithm}
\caption{Synthetic Data Simulation}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$\Delta t$, $T$, $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from homogeneous Poisson process $(\tau^\star_{i(j)})$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample a series of Brownian motion $(\hat{W}_t)$
\STATE Initialize $\ell^{i(j)}=0$, $y_0 = 0$, $\hat{y}_0 = 0$, $\tilde{y}_t=0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \STATE $y_{t+\Delta t} \gets$ (\ref{eq-state-dynamics}); $\tilde{y}_{t+\Delta t}$ $\gets$ (\ref{eq-fintered-y-update})
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta t)$} 
        \IF {$u_k^{i(j)} < \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta t} \gets $ (\ref{eq-leaderboard-gap})
        \ENDIF
    \ENDFOR
\ENDFOR
\STATE Fill in all missing entries in $(\hat{y}_t)$ by propagating the last observed value.
\STATE \textbf{Output:} $(\tilde{y}_t)$, $(\hat{y}_t)$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(m_{i(j)}(\tilde{y}_t, t))$
\end{algorithmic}
\end{algorithm}
